### 2016-09-23 results.tex
counterexample for SS-privacy of bigram linear

\end{theorem}
\begin{proof}(Sketch.)
On input the set~$S$ produced by~$A$, the $\Rep$ algorithm turns $x_1=$'cab', $x_2=$'bab' and $x_3$ into their respective bigram sets: $B_{x_1}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{b}\sqcup\}$, $B_{x_2}=\{\sqcup\mathrm{b},\mathrm{ba},\mathrm{ab}, \mathrm{b}\sqcup \}$; the set $B_{x_3}$ will be either $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, or $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, each with probability 1/2.  It then produces $alpha$-bit arrays $M_1, M_2, M_3$ by hashing the corresponding bigram sets using the hash functions $h_j(s)=\rho_1(s)+ j\rho_2(s) \bmod m$.  Note that for sufficiently large~$m$, each of $M_1,M_2$ will contain exactly $4k$ positions set to 1; this is with overwhelming probability (up to collisions in the hash functions for different bigrams within a given bigram set).   Likewise, $M_{1,2}=M_1 \vee M_2$ will have exactly $6k$ positions set to 1, because $B_{x_1}$ and $B_{x_2}$ share $\mathrm{ab}$ and $\mathrm{a}\sqcup$.

>>>>

\end{theorem}
\begin{proof}(Sketch.)
On input the set~$S$ produced by~$A$, the $\Rep$ algorithm turns $x_1=$'cab', $x_2=$'bab' and $x_3$ into their respective bigram sets: $B_{x_1}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{b}\sqcup\}$, $B_{x_2}=\{\sqcup\mathrm{b},\mathrm{ba},\mathrm{ab}, \mathrm{b}\sqcup \}$; the set $B_{x_3}$ will be either $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, or $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, each with probability 1/2.  It then produces $\alpha$-bit arrays $M_1, M_2, M_3$ by hashing the corresponding bigram sets using the hash functions $h_j(s)=\rho_1(s)+ j\rho_2(s) \bmod m$.  Note that for sufficiently large~$m$, each of $M_1,M_2$ will contain exactly $4k$ positions set to 1; this is with overwhelming probability (up to collisions in the hash functions for different bigrams within a given bigram set).   Likewise, $M_{1,2}=M_1 \vee M_2$ will have exactly $6k$ positions set to 1, because $B_{x_1}$ and $B_{x_2}$ share $\mathrm{ab}$ and $\mathrm{a}\sqcup$.
